### 2023-09-29 appendices/supplementary_retrospective.tex
Work on background and main contributions
Updates to citation commands and footnotes

\begin{table}[t]
    \centering
    \caption{Overview of hyperparameters used for training the text classification models.}
    \label{tab_retrospective:tableA1-hyperparameters}
    \resizebox*{0.98\textwidth}{!}{%
    \begin{tabular}{l|l|l}
        \toprule

@@

\subsubsection{Bag-of-words selection}

@@

We used standard methods for significance testing and computing the confidence intervals. We used approximate methods owing to data size and to maintain computational feasibility \cite{dwass_modified_1957,eden_validity_1933}

>>>>

\begin{table}[t]
    \centering
    \caption{Overview of hyperparameters for training text classification models.}
    \label{tab_retrospective:tableA1-hyperparameters}
    \resizebox*{0.98\textwidth}{!}{%
    \begin{tabular}{l|l|l}
        \toprule

@@

        \bottomrule
    \end{tabular}%
    \vspace{-2mm}
    }
\end{table}

\paragraph{Bag-of-words selection}

@@

We used standard methods for significance testing and computing the confidence intervals. We used approximate methods owing to data size and to maintain computational feasibility \parencite{dwass_modified_1957,eden_validity_1933}
